A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-18 papers/execution-model/model.tex
slight revisions in section 2

For concreteness, Listing~\ref{lst:auction-contract-header} shows the
header of an auction contract in Michelson \cite{michelson}. The
\lstinline/parameter/ clause specifies the contract's parameter
type. It is a sum type (indicated by \lstinline/or/) and each
alternative constitutes an entrypoint, named \lstinline/%close/ and
\lstinline/%bid/. The caller selects the entrypoint by injecting the argument into the
\lstinline/left/ or \lstinline/right/ summand. Entrypoint \lstinline/%close/ takes a \lstinline{unit}
parameter and \lstinline/%bid/ takes an amount of tokens of type \lstinline{mutez}.
The \lstinline/storage/ clause declares the state of the contract,
which is a nested pair type indicating whether bidding is allowed (\lstinline{bool}), the address of the
contract owner (to prohibit unauthorized calls to \lstinline/%close/),
the highest bid (of type \lstinline{mutez}), and the bidder's address.
\begin{lstlisting}[language=michelson,numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
parameter (or (unit %close)
              (mutez %bid)); # participant's bid
storage (pair
          (pair bool address)  # bidding allowed, contract owner
          (pair mutez address) # highest bid, bidder's address
        );
\end{lstlisting}

To avoid too much detail, we just outline the implementation of the entrypoints. The
\lstinline/%close/ entrypoint first checks its sender's address
against the owner's address in the store. Then it transfers the funds
to the owner, closes the contract by clearing the bidding flag, and
leaves it to the owner to deliver the
goods.\footnote{For simplicity we elide safeguarding by a third-party oracle.}
The \lstinline/%bid/ entrypoint immediately returns each bid that is not higher
than the existing highest bid. Otherwise, it keeps the funds
transferred, returns the previous highest bid to its owner, and stores
the current bid as the new highest bid.

@@

First the code that creates an auction contract and closes it after 48 hours. 
\begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
let initial_store = ((true, my_address), (1, my_address))
let contract = Cl.originate(auction_script, 1, initial_store)
Time.sleep(48 * 3600);               (* 48h in seconds *)
Cl.call_contract(contract, left ()); (* entrypoint %close *)
\end{lstlisting}
We assume that \lstinline/Cl/ is the module containing the contract
library,  \lstinline/originate/ deploys its argument contract along
with the provided funds and the \lstinline/initial_store/, 
\lstinline{auction_script} is the contract from Listing~\ref{lst:auction-contract-header}, and 
\lstinline{call_contract} invokes a contract with a parameter.

>>>>

For concreteness, Listing~\ref{lst:auction-contract-header} shows the
header of an auction contract in Michelson \cite{michelson}. The
\lstinline/parameter/ clause specifies the contract's parameter
type. It is a sum type (indicated by \lstinline/or/) and each
alternative constitutes an entrypoint, named \lstinline/%close/ and
\lstinline/%bid/. The caller selects the entrypoint by injecting the argument into the
\lstinline/left/ or \lstinline/right/ summand. Both entrypoints take a \lstinline{unit}
parameter. The \lstinline/%bid/ entrypoint considers the transferred
tokens as the bid.
The \lstinline/storage/ clause declares the state of the contract,
which is a nested pair type indicating whether bidding is allowed
(\lstinline{bool}), the address of the contract owner (to prohibit
unauthorized calls to \lstinline/%close/), and the bidder's
address. The highest bid corresponds to the token balance of the contract.
\begin{lstlisting}[language=michelson,numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
parameter (or (unit %close)
              (unit %bid)); # bid in transfer
storage (pair bool          # bidding allowed
         (pair address      #  contract owner
          address           # highest bidder's address
        ));
\end{lstlisting}

To avoid too much detail, we just outline the implementation of the entrypoints. The
\lstinline/%close/ entrypoint first checks its sender's address
against the owner's address in the store. Then it transfers the funds
to the owner, closes the contract by clearing the bidding flag, and
leaves it to the owner to deliver the
goods.\footnote{For simplicity we elide safeguarding by a third-party oracle.}
The \lstinline/%bid/ entrypoint immediately returns each bid that is not higher
than the existing highest bid. Otherwise, it keeps the funds
transferred, returns the previous highest bid to its owner, and stores
the current bidder as the new highest bidder.

@@

First the code that creates an auction contract and closes it after 48 hours. 
\begin{lstlisting}[language=Caml,numbers=none,basicstyle=\small]
let _ = Cl.set_authority (my_address)
let initial_store = (true, (my_address, my_address))
let contract = Cl.originate(auction_script, 1, initial_store)
Time.sleep(48 * 3600);               (* 48h in seconds *)
Cl.call_contract(contract, left ()); (* entrypoint %close *)
\end{lstlisting}
We assume that \lstinline/Cl/ is the module containing the contract
library, \lstinline{set_authority} sets the sender address for
upcoming operations,  \lstinline/originate/ deploys its argument contract along
with the provided funds of one token and the \lstinline/initial_store/, 
\lstinline{auction_script} is the contract from Listing~\ref{lst:auction-contract-header}, and 
\lstinline{call_contract} invokes a contract with a parameter. The
\lstinline{initial_store} sets the bidding flag, and both owner and
highest bidder to the sender account.
